Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-06 ms.tex
Reincorporating some of nicks changes.

Realistic variations (``burstiness") in the star formation history will result in lower heating rates.  Figure \ref{app:windheat}  shows the heating rate as a function of average black hole mass also for cases in which the current ($z = 0$) star formation is suppressed by a factor $\epsilon_{\rm burst}$ from its average $z = 0$ value for a characteristic timescale $\tau_{\rm var}$ (for details, see Appendix \ref{fig:}).  For low values of $\tau_{\rm var} \lesssim 10^{7}$ yr we see that $v_{w}^{\star}$ is reduced by at most a factor of $\sim 2$ from its average value, even for very small values of $\epsilon_{\rm burst}=$... , while for $\tau_{\rm var} \gtrsim 10^{8}$ yr, wind heating is reduced significantly.  We conclude that variations in the nuclear star formation rate on timescales short compared to the dynamical timescale of the galaxy are unlikely to significantly affect our results.  {\bf BDM: augment/fix this - its just schematic till nick provides his figure}

>>>>

Realistic variations (``burstiness") in the star formation history
will often result in lower heating rates.  Figure \ref{NickPlot2}
shows the heating rate as a function of average black hole mass for
non-fiducial cases in which the current ($z = 0$) star formation is
suppressed by a factor $\zeta$ from its average $z = 0$ value, for a
characteristic timescale $t_{\rm scale}$ (for details, see Appendix
\ref{app:windheat}).  For $t_{\rm scale} \lesssim 10^{7}$ yr, we see
that $v_{\rm w}^{\star}$ is reduced by at most a factor of $\approx 2$
from its average value, even for huge drops in the star formation rate
($\zeta \sim 10^{-3}$).  However, burstiness in the star formation
history over longer timescales can suppress heating more
significantly.  When $t_{\rm scale} \gtrsim 10^8~{\rm yr}$, $v_{\rm
  w}^\star$ becomes very sensitive to $\zeta$: at $\zeta=0.1$, $v_{\rm
  w}^\star \approx 500~{\rm km~s}^{-1}$ in most galaxies, but for
smaller $\zeta$, $v_{\rm w}^\star \approx 200~{\rm km~s}^{-1}$ (an
exception to this is in galactic nuclei with $M_\bullet \gtrsim
5\times 10^8~M_\odot$, where heating is stabilized by SN Ia).  Our use
of average cosmic star formation histories is appropriate provided
local variations are either on short timescales ($t_{\rm scale}
\lesssim 10^7~{\rm yr}$), or limited in magnitude ($\zeta \gtrsim
0.1$).  If both of these conditions are violated, then the effective
heating rates for all but the most massive galaxies (where Ia
explosions dominate) will fall by a factor $\approx 5$ from our
fiducial volumetric averages, taken from \citet{MosterNaab+:2013a}.

{\bf NCS: is this reduced heating rate thermally unstable under Aleksey's revised formula?  We should comment}
